### 2018-05-03 doc/paper.tex
Adding some more "insight" to the proof.
I used code to prove the claim to myself about how
the l-tilde terms relate to each other. We can actually
be a bit more specific. For example, write

   l1 = e1 + ... + e3 + rho b
   l2 = f1 + ... + f8 + rho db

then we can actually show that

   tilde(l2) <= gamma5 e1 + gamma5 e2 + gamma4 e3 +
                gamma4 (rho b) +
                gamma3[(1 - s) db{j} + s db{j + 1}].

To extend the example, write

   l3 = g1 + ... + g13 + rho d2b

then we can actually show that

   tilde(l3) <= gamma10 f1 + gamma10 f2 + gamma9 f3 + gamma8 f4 +

\usepackage{amsthm,amssymb,amsmath}
%% H/T: https://tex.stackexchange.com/a/202168/32270
\usepackage{textcomp}
%% H/T: https://tex.stackexchange.com/a/56877/32270
\usepackage{algorithm}
\usepackage{algpseudocode}
%% H/T: https://tex.stackexchange.com/a/244805
\usepackage{booktabs,siunitx}
%% H/T: https://tex.stackexchange.com/a/4217/32270
\usepackage{mathtools}
%% H/T: https://tex.stackexchange.com/a/33869/32270
\makeatletter
\newenvironment{breakablealgorithm}
  {% \begin{breakablealgorithm}
   \begin{center}
     \refstepcounter{algorithm}% New algorithm
     \hrule height.8pt depth0pt \kern2pt% \@fs@pre for \@fs@ruled
     \renewcommand{\caption}[2][\relax]{% Make a new \caption
       {\raggedright\textbf{\ALG@name~\thealgorithm} ##2\par}%
       \ifx\relax##1\relax % #1 is \relax
         \addcontentsline{loa}{algorithm}{\protect\numberline{\thealgorithm}##2}%
       \else % #1 is not \relax
         \addcontentsline{loa}{algorithm}{\protect\numberline{\thealgorithm}##1}%
       \fi
       \kern2pt\hrule\kern2pt
     }
  }{% \end{breakablealgorithm}
     \kern2pt\hrule\relax% \@fs@post for \@fs@ruled
   \end{center}
  }
\makeatother
%% H/T: https://tex.stackexchange.com/a/28334/32270
\usepackage{chngcntr}
\counterwithin{figure}{section}
\counterwithin{table}{section}
\counterwithin{equation}{section}
\counterwithin{algorithm}{section}
%% H/T: https://tex.stackexchange.com/a/202047/32270
%%      https://tex.stackexchange.com/a/32463/32270
\usepackage[labelfont=bf]{caption}
%% H/T: https://tex.stackexchange.com/a/71153/32270
\usepackage[nottoc,notlot,notlof]{tocbibind}

@@

\begin{theorem}[\cite{Ogita2005}]\label{thm:eft}
For \(a, b \in \mathbf{F}\) and \(P, \pi, S, \sigma \in \mathbf{F}\),
\texttt{TwoSum} and \texttt{TwoProd} satisfy
\begin{itemize}
  \item \(\left[S, \sigma\right] = \mathtt{TwoSum}(a, b)\), \(x = \fl{a + b}\),
      \(S + \sigma = a + b\), \(\sigma \leq \mach \left|S\right|\),
      \(\sigma \leq \mach \left|a + b\right|\)
  \item \(\left[P, \pi\right] = \mathtt{TwoProd}(a, b)\),
      \(P = \fl{a \times b}\), \(P + \pi = a \times b\),
      \(\pi \leq \mach \left|P\right|\),
      \(\pi \leq \mach \left|a \times b\right|\).
\end{itemize}
The letters \(\sigma\) and \(\pi\) are used to indicate that the
errors came from sum and product, respectively. See the appendix
in Section~\ref{sec:appendix-eft} for implementation details.
\end{theorem}

@@

The relative condition number of the evaluation of \(p(s) = \sum_{j = 0}^n
b_j B_{j, n}(s)\) in Bernstein form used in this paper is (see
\cite{Mainar1999}, \cite{Farouki1987}):
\begin{equation}
\cond{p, s} = \frac{\widetilde{p}(s)}{
  \left|p(s)\right|} = \frac{\sum_j \left|b_j\right| B_{j, n}(s)}{
  \left|p(s)\right|},
\end{equation}
where \(B_{j, n} \geq 0\).

@@

When computing \(\cdb{F}\) (i.e. the error after
\(F\) stages of filtering)
there will be several sources of round-off. In particular, there will be
\begin{itemize}
\item errors when computing \(\widehat{\ell}_{F, j}^{(k)}\) from the
  terms in \(\ell_{F, j}^{(k)}\)
\item an error
for the ``missing'' \(\rho \cdot \cdb{F}_j^{(k + 1)}\) in
\((1 - s) \cdot \cdb{F}_j^{(k + 1)}\)
\item an error from the product
  \(\widehat{r} \otimes \cdb{F}_j^{(k + 1)}\)
\item an error from the product
  \(s \otimes \cdb{F}_{j + 1}^{(k + 1)}\)
\item two errors from the two \(\oplus\) when combining the three
  terms in
  \(\widehat{\ell}_{F, j}^{(k)} \oplus
  \left(s \otimes \cdb{F}_{j + 1}^{(k + 1)}\right) \oplus
  \left(\widehat{r} \otimes \cdb{F}_j^{(k + 1)}\right)\)
\end{itemize}
For example, in~\eqref{ell-j}:
%% H/T: https://tex.stackexchange.com/a/154333/32270
\begin{equation}
\ell_{1, j}^{(k)} =
    \underbrace{\vphantom{\rho \cdot \widehat{b}_j^{(k + 1)}} \pi_1}_{
        \vphantom{(1 - s) \widehat{b}_j^{(k + 1)}}
        P_1 = \widehat{r} \otimes \widehat{b}_j^{(k + 1)}} +
    \underbrace{\vphantom{\rho \cdot \widehat{b}_j^{(k + 1)}} \pi_2}_{
        \vphantom{(1 - s) \widehat{b}_j^{(k + 1)}}
        P_2 = s \otimes \widehat{b}_{j + 1}^{(k + 1)}} +
    \underbrace{\vphantom{\rho \cdot \widehat{b}_j^{(k + 1)}} \sigma_3}_{
        \vphantom{(1 - s) \widehat{b}_j^{(k + 1)}}
        P_1 \oplus P_2} +
    \underbrace{\rho \cdot \widehat{b}_j^{(k + 1)}}_{
        (1 - s) \widehat{b}_j^{(k + 1)}}
\end{equation}
After each stage, we'll always have
\begin{equation}
\ell_{F, j}^{(k)} = e_1 + e_2 + \cdots + e_M + \rho \cdot
\cdb{F - 1}_j^{(k + 1)}
\end{equation}
where the terms \(e_1, \ldots, e_M\) come from using \texttt{TwoSum} and
\texttt{TwoProd} when computing \(\cdb{F - 1}_j^{(k)}\)
and the \(\rho\) term comes from the roundoff
in \(1 \ominus s\) when multiplying \((1 - s)\) by
\(\cdb{F - 1}_j^{(k + 1)}\). With this in mind, we
can define an EFT (\texttt{LocalErrorEFT}) that computes
\(\widehat{\ell}\) and tracks all round-off errors generated in
the process:

\begin{breakablealgorithm}
  \caption{\textit{EFT for computing the local error.}}

  \begin{algorithmic}
    \Function{\(\left[\eta, \widehat{\ell}\right] =
        \mathtt{LocalErrorEFT}\)}{$e, \rho, \delta b$}
      \State \(M = \texttt{length}(e)\)
      \\
      \State \(\left[\widehat{\ell}, \eta_1\right] =
          \mathtt{TwoSum}(e_1, e_2)\)
      \For{\(j = 3, \ldots, M\)}
        \State \(\left[\widehat{\ell}, \eta_{j - 1}\right] =
            \mathtt{TwoSum}\left(\widehat{\ell}, e_j\right)\)
      \EndFor
      \\
      \State \(\left[P, \eta_M\right] =
          \mathtt{TwoProd}\left(\rho, \delta b\right)\)
      \State \(\left[\widehat{\ell}, \eta_{M + 1}\right] =
          \mathtt{TwoSum}\left(\widehat{\ell}, P\right)\)
    \EndFunction
  \end{algorithmic}
\end{breakablealgorithm}

\noindent With this EFT in place, we can perform \((K - 1)\)
error filtrations:

@@

  \begin{algorithmic}
    \Function{\(\mathtt{res} = \mathtt{CompDeCasteljauK}\)}{$b, s, K$}
      \State \(n = \texttt{length}(b) - 1\)
      \State \(\left[\widehat{r}, \rho\right] = \mathtt{TwoSum}(1, -s)\)
      \\
      \For{\(j = 0, \ldots, n\)}
        \State \(\widehat{b}_j^{(n)} = b_j\)
        \For{\(F = 1, \ldots, K - 1\)}
          \State \(\cdb{F}_j^{(n)} = 0\)
        \EndFor
      \EndFor
      \\
      \For{\(k = n - 1, \ldots, 0\)}
        \For{\(j = 0, \ldots, k\)}
          \State \(\left[P_1, \pi_1\right] = \mathtt{TwoProd}\left(
              \widehat{r}, \widehat{b}_j^{(k + 1)}\right)\)
          \State \(\left[P_2, \pi_2\right] = \mathtt{TwoProd}\left(
              s, \widehat{b}_{j + 1}^{(k + 1)}\right)\)
          \State \(\left[\widehat{b}_j^{(k)}, \sigma_3\right] =
              \mathtt{TwoSum}(P_1, P_2)\)
          \\
          \State \(e = \left[\pi_1, \pi_2, \sigma_3\right]\)
          \State \(\delta b = \widehat{b}_j^{(k + 1)}\)
          \\
          \For{\(F = 1, \ldots, K - 2\)}
            \State \(\left[\eta, \widehat{\ell}\right] =
                \mathtt{LocalErrorEFT}(e, \rho, \delta b)\)
            \State \(M = \texttt{length}(\eta)\)
            \\
            \State \(\left[P_1, \eta_{M + 1}\right] = \mathtt{TwoProd}\left(
                s, \cdb{F}_{j + 1}^{(k + 1)}\right)\)
            \State \(\left[S_2, \eta_{M + 2}\right] =
                \mathtt{TwoSum}\left(\widehat{\ell}, P_1\right)\)
            \State \(\left[P_3, \eta_{M + 3}\right] = \mathtt{TwoProd}\left(
                \widehat{r}, \cdb{F}_j^{(k + 1)}\right)\)
            \State \(\left[\cdb{F}_j^{(k)}, \eta_{M + 4}\right]
                = \mathtt{TwoSum}\left(S_2, P_3\right)\)
            \\
            \State \(e = \eta\)
            \State \(\delta b = \cdb{F}_j^{(k + 1)}\)
          \EndFor
          \\
          \State \(\widehat{\ell} =
                \mathtt{LocalError}(e, \rho, \delta b)\)
          \State \(\cdb{K - 1}_j^{(k)} =
              \widehat{\ell} \oplus
              \left(s \otimes \cdb{K - 1}_{j + 1}^{(k + 1)}
              \right) \oplus
              \left(\widehat{r} \otimes
              \cdb{K - 1}_j^{(k + 1)}\right)\)
        \EndFor
      \EndFor
      \\
      \State \(\mathtt{res} = \widehat{b}_0^{(0)}\)
      \For{\(F = 1, \ldots, K - 1\)}
        \State \(\mathtt{res} = \mathtt{res} \oplus
            \cdb{F}_0^{(0)}\)
      \EndFor
    \EndFunction
  \end{algorithmic}
\end{breakablealgorithm}

@@

First, note that \(\widehat{r} = (1 - s)(1 + \theta_1)\). Due to this,
we put the \(\widehat{r}\) term at the end of each update step to reduce
the amount of round-off:
\begin{align}
  \cdb{F}_j^{(k)} &=
  \widehat{\ell}_{F, j}^{(k)} \oplus
  \left(s \otimes \cdb{F}_{j + 1}^{(k + 1)}\right) \oplus
  \left(\widehat{r} \otimes \cdb{F}_j^{(k + 1)}\right) \\
&= (1 - s) \cdot \cdb{F}_j^{(k + 1)}(1 + \theta_3) +
  s \cdot \cdb{F}_{j + 1}^{(k + 1)}(1 + \theta_3) +
  \widehat{\ell}_{F, j}^{(k)} (1 + \theta_2) \\
\Longrightarrow \cdb{F}^{(k)} &=
  U_{k + 1}(s) \cdb{F}^{(k + 1)}(1 + \theta_3) +
  \widehat{\ell}_{F}^{(k)} (1 + \theta_2).
\end{align}
This is quite similar to the relationship satisfied in
exact arithmetic:
\begin{equation}
\db{F}^{(k)} = U_{k + 1}(s) \db{F}^{(k + 1)} + \ell_{F}^{(k)}.
\end{equation}

@@

\section{Appendix: EFT Algorithms}\label{sec:appendix-eft}

@@

>>>>

\usepackage{amsthm,amssymb,amsmath}
%% https://tex.stackexchange.com/a/396829/32270
\allowdisplaybreaks
%% H/T: https://tex.stackexchange.com/a/202168/32270
\usepackage{textcomp}
%% H/T: https://tex.stackexchange.com/a/56877/32270
\usepackage{algorithm}
\usepackage{algpseudocode}
%% H/T: https://tex.stackexchange.com/a/244805
\usepackage{booktabs,siunitx}
%% H/T: https://tex.stackexchange.com/a/4217/32270
\usepackage{mathtools}
%% H/T: https://tex.stackexchange.com/a/33869/32270
\makeatletter
\newenvironment{breakablealgorithm}
  {% \begin{breakablealgorithm}
   \begin{center}
     \refstepcounter{algorithm}% New algorithm
     \hrule height.8pt depth0pt \kern2pt% \@fs@pre for \@fs@ruled
     \renewcommand{\caption}[2][\relax]{% Make a new \caption
       {\raggedright\textbf{\ALG@name~\thealgorithm} ##2\par}%
       \ifx\relax##1\relax % #1 is \relax
         \addcontentsline{loa}{algorithm}{\protect\numberline{\thealgorithm}##2}%
       \else % #1 is not \relax
         \addcontentsline{loa}{algorithm}{\protect\numberline{\thealgorithm}##1}%
       \fi
       \kern2pt\hrule\kern2pt
     }
  }{% \end{breakablealgorithm}
     \kern2pt\hrule\relax% \@fs@post for \@fs@ruled
   \end{center}
  }
\makeatother
%% H/T: https://tex.stackexchange.com/a/28334/32270
\usepackage{chngcntr}
\counterwithin{figure}{section}
\counterwithin{table}{section}
\counterwithin{equation}{section}
\counterwithin{algorithm}{section}
%% H/T: https://tex.stackexchange.com/a/202047/32270
%%      https://tex.stackexchange.com/a/32463/32270
\usepackage[labelfont=bf]{caption}
%% H/T: https://tex.stackexchange.com/a/71153/32270
\usepackage[nottoc,notlot,notlof]{tocbibind}

@@

\begin{theorem}[\cite{Ogita2005}]\label{thm:eft}
For \(a, b \in \mathbf{F}\) and \(P, \pi, S, \sigma \in \mathbf{F}\),
\texttt{TwoSum} and \texttt{TwoProd} satisfy
\begin{itemize}
  \item \(\left[S, \sigma\right] = \mathtt{TwoSum}(a, b)\), \(x = \fl{a + b}\),
      \(S + \sigma = a + b\), \(\sigma \leq \mach \left|S\right|\),
      \(\sigma \leq \mach \left|a + b\right|\)
  \item \(\left[P, \pi\right] = \mathtt{TwoProd}(a, b)\),
      \(P = \fl{a \times b}\), \(P + \pi = a \times b\),
      \(\pi \leq \mach \left|P\right|\),
      \(\pi \leq \mach \left|a \times b\right|\).
\end{itemize}
The letters \(\sigma\) and \(\pi\) are used to indicate that the
errors came from sum and product, respectively. See the appendix
in Section~\ref{sec:appendix-algo} for implementation details.
\end{theorem}

@@

The relative condition number of the evaluation of \(p(s) = \sum_{j = 0}^n
b_j B_{j, n}(s)\) in Bernstein form used in this paper is (see
\cite{Mainar1999}, \cite{Farouki1987}):
\begin{equation}
\cond{p, s} = \frac{\widetilde{p}(s)}{\left|p(s)\right|},
\end{equation}
where \(B_{j, n}(s) \geq 0\) and
\(\widetilde{p}(s) \coloneqq \sum_{j = 0}^n \left|b_j\right| B_{j, n}(s)\).

@@

When computing \(\cdb{F}\) (i.e. the error after
\(F\) stages of filtering)
there will be several sources of round-off. In particular, there will be
\begin{itemize}
\item errors when computing \(\widehat{\ell}_{F, j}^{(k)}\) from the
  terms in \(\ell_{F, j}^{(k)}\)
\item an error
for the ``missing'' \(\rho \cdot \cdb{F}_j^{(k + 1)}\) in
\((1 - s) \cdot \cdb{F}_j^{(k + 1)}\)
\item an error from the product
  \(\widehat{r} \otimes \cdb{F}_j^{(k + 1)}\)
\item an error from the product
  \(s \otimes \cdb{F}_{j + 1}^{(k + 1)}\)
\item two errors from the two \(\oplus\) when combining the three
  terms in
  \(\widehat{\ell}_{F, j}^{(k)} \oplus
  \left(s \otimes \cdb{F}_{j + 1}^{(k + 1)}\right) \oplus
  \left(\widehat{r} \otimes \cdb{F}_j^{(k + 1)}\right)\)
\end{itemize}
For example, in~\eqref{ell-j}:
%% H/T: https://tex.stackexchange.com/a/154333/32270
\begin{equation}
\ell_{1, j}^{(k)} =
    \underbrace{\vphantom{\rho \cdot \widehat{b}_j^{(k + 1)}} \pi_1}_{
        \vphantom{(1 - s) \widehat{b}_j^{(k + 1)}}
        P_1 = \widehat{r} \otimes \widehat{b}_j^{(k + 1)}} +
    \underbrace{\vphantom{\rho \cdot \widehat{b}_j^{(k + 1)}} \pi_2}_{
        \vphantom{(1 - s) \widehat{b}_j^{(k + 1)}}
        P_2 = s \otimes \widehat{b}_{j + 1}^{(k + 1)}} +
    \underbrace{\vphantom{\rho \cdot \widehat{b}_j^{(k + 1)}} \sigma_3}_{
        \vphantom{(1 - s) \widehat{b}_j^{(k + 1)}}
        P_1 \oplus P_2} +
    \underbrace{\rho \cdot \widehat{b}_j^{(k + 1)}}_{
        (1 - s) \widehat{b}_j^{(k + 1)}}
\end{equation}
After each stage, we'll always have
\begin{equation}
\ell_{F, j}^{(k)} = e_1 + \cdots + e_{5F - 2} + \rho \cdot
\cdb{F - 1}_j^{(k + 1)}
\end{equation}
where the terms \(e_1, \ldots, e_{5F - 2}\) come from using \texttt{TwoSum}
and \texttt{TwoProd} when computing \(\cdb{F - 1}_j^{(k)}\)
and the \(\rho\) term comes from the roundoff
in \(1 \ominus s\) when multiplying \((1 - s)\) by
\(\cdb{F - 1}_j^{(k + 1)}\). With this in mind, we
can define an EFT (\texttt{LocalErrorEFT}) that computes
\(\widehat{\ell}\) and tracks all round-off errors generated in
the process:

\begin{breakablealgorithm}
  \caption{\textit{EFT for computing the local error.}}
  \label{alg:local-error-eft}

  \begin{algorithmic}
    \Function{\(\left[\eta, \widehat{\ell}\right] =
        \mathtt{LocalErrorEFT}\)}{$e, \rho, \delta b$}
      \State \(L = \texttt{length}(e)\)
      \\
      \State \(\left[\widehat{\ell}, \eta_1\right] =
          \mathtt{TwoSum}(e_1, e_2)\)
      \For{\(j = 3, \ldots, L\)}
        \State \(\left[\widehat{\ell}, \eta_{j - 1}\right] =
            \mathtt{TwoSum}\left(\widehat{\ell}, e_j\right)\)
      \EndFor
      \\
      \State \(\left[P, \eta_L\right] =
          \mathtt{TwoProd}\left(\rho, \delta b\right)\)
      \State \(\left[\widehat{\ell}, \eta_{L + 1}\right] =
          \mathtt{TwoSum}\left(\widehat{\ell}, P\right)\)
    \EndFunction
  \end{algorithmic}
\end{breakablealgorithm}

\noindent With this EFT in place\footnote{And the related
\texttt{LocalError} in Algorithm~\ref{alg:local-error}}, we can
perform \((K - 1)\) error filtrations:

@@

  \begin{algorithmic}
    \Function{\(\mathtt{res} = \mathtt{CompDeCasteljauK}\)}{$b, s, K$}
      \State \(n = \texttt{length}(b) - 1\)
      \State \(\left[\widehat{r}, \rho\right] = \mathtt{TwoSum}(1, -s)\)
      \\
      \For{\(j = 0, \ldots, n\)}
        \State \(\widehat{b}_j^{(n)} = b_j\)
        \For{\(F = 1, \ldots, K - 1\)}
          \State \(\cdb{F}_j^{(n)} = 0\)
        \EndFor
      \EndFor
      \\
      \For{\(k = n - 1, \ldots, 0\)}
        \For{\(j = 0, \ldots, k\)}
          \State \(\left[P_1, \pi_1\right] = \mathtt{TwoProd}\left(
              \widehat{r}, \widehat{b}_j^{(k + 1)}\right)\)
          \State \(\left[P_2, \pi_2\right] = \mathtt{TwoProd}\left(
              s, \widehat{b}_{j + 1}^{(k + 1)}\right)\)
          \State \(\left[\widehat{b}_j^{(k)}, \sigma_3\right] =
              \mathtt{TwoSum}(P_1, P_2)\)
          \\
          \State \(e = \left[\pi_1, \pi_2, \sigma_3\right]\)
          \State \(\delta b = \widehat{b}_j^{(k + 1)}\)
          \\
          \For{\(F = 1, \ldots, K - 2\)}
            \State \(\left[\eta, \widehat{\ell}\right] =
                \mathtt{LocalErrorEFT}(e, \rho, \delta b)\)
            \State \(L = \texttt{length}(\eta)\)
            \\
            \State \(\left[P_1, \eta_{L + 1}\right] = \mathtt{TwoProd}\left(
                s, \cdb{F}_{j + 1}^{(k + 1)}\right)\)
            \State \(\left[S_2, \eta_{L + 2}\right] =
                \mathtt{TwoSum}\left(\widehat{\ell}, P_1\right)\)
            \State \(\left[P_3, \eta_{L + 3}\right] = \mathtt{TwoProd}\left(
                \widehat{r}, \cdb{F}_j^{(k + 1)}\right)\)
            \State \(\left[\cdb{F}_j^{(k)}, \eta_{L + 4}\right]
                = \mathtt{TwoSum}\left(S_2, P_3\right)\)
            \\
            \State \(e = \eta\)
            \State \(\delta b = \cdb{F}_j^{(k + 1)}\)
          \EndFor
          \\
          \State \(\widehat{\ell} =
                \mathtt{LocalError}(e, \rho, \delta b)\)
          \State \(\cdb{K - 1}_j^{(k)} =
              \widehat{\ell} \oplus
              \left(s \otimes \cdb{K - 1}_{j + 1}^{(k + 1)}
              \right) \oplus
              \left(\widehat{r} \otimes
              \cdb{K - 1}_j^{(k + 1)}\right)\)
        \EndFor
      \EndFor
      \\
      \State \(\mathtt{res} = \widehat{b}_0^{(0)}\)
      \For{\(F = 1, \ldots, K - 1\)}
        \State \(\mathtt{res} = \mathtt{res} \oplus
            \cdb{F}_0^{(0)}\)
      \EndFor
    \EndFunction
  \end{algorithmic}
\end{breakablealgorithm}

@@

To be able to express the algorithm in matrix form, we define
the vectors
\begin{gather}
b^{(k)} = \left[\begin{array}{c c c} b_0^{(k)} & \cdots &
b_k^{(k)}\end{array}\right]^T, \quad
\widehat{b}^{(k)} = \left[\begin{array}{c c c} \widehat{b}_0^{(k)} & \cdots &
\widehat{b}_k^{(k)}\end{array}\right]^T, \\
\db{F}^{(k)} = \left[\begin{array}{c c c} \db{F}_0^{(k)} & \cdots &
\db{F}_k^{(k)}\end{array}\right]^T, \quad
\cdb{F}^{(k)} = \left[\begin{array}{c c c} \cdb{F}_0^{(k)} & \cdots &
\cdb{F}_k^{(k)}\end{array}\right]^T, \\
\ell_{F}^{(k)} = \left[\begin{array}{c c c} \ell_{F, 0}^{(k)} & \cdots &
\ell_{F, k}^{(k)}\end{array}\right]^T, \quad
\widehat{\ell}_{F}^{(k)} = \left[\begin{array}{c c c}
\widehat{\ell}_{F, 0}^{(k)} & \cdots &
\widehat{\ell}_{F, k}^{(k)}\end{array}\right]^T
\end{gather}
and the reduction matrices:
\begin{equation}
U_k = U_k(s) = \left[\begin{array}{c c c c c c}
    1 - s  & s      & 0      & \cdots & \cdots & 0      \\
    0      & 1 - s  & s      & \ddots &        & \vdots \\
    \vdots & \ddots & \ddots & \ddots & \ddots & \vdots \\
    \vdots &        & \ddots & \ddots & \ddots & 0 \\
    0      & \cdots & \cdots & 0      & 1 - s  & s
\end{array}\right] \in \mathbf{R}^{k \times (k + 1)}.
\end{equation}
With this, we can express the compensated de Casteljau algorithm as
\begin{align}
b^{(k)} &= U_{k + 1} b^{(k + 1)} \\
\Longrightarrow b^{(0)} &= U_1 \cdots U_n b^{(n)} \\
\db{F}^{(k)} &= U_{k + 1} \db{F}^{(k + 1)} + \ell_{F}^{(k)} \\
\Longrightarrow \db{F}^{(0)} &= \sum_{k = 0}^{n - 1}
U_1 \cdots U_k \ell_F^{(k)} = \sum_{k = 0}^{n - 1}
\left[\sum_{j = 0}^k \ell_{F, j}^{(k)} B_{j, k}(s)\right].
\end{align}
For the inexact equivalent of these things, first note that
\(\widehat{r} = (1 - s)(1 + \theta_1)\). Due to this,
we put the \(\widehat{r}\) term at the end of each update step to reduce
the amount of round-off:
\begin{align}
  \cdb{F}_j^{(k)} &=
  \widehat{\ell}_{F, j}^{(k)} \oplus
  \left(s \otimes \cdb{F}_{j + 1}^{(k + 1)}\right) \oplus
  \left(\widehat{r} \otimes \cdb{F}_j^{(k + 1)}\right) \\
&= (1 - s) \cdot \cdb{F}_j^{(k + 1)}(1 + \theta_3) +
  s \cdot \cdb{F}_{j + 1}^{(k + 1)}(1 + \theta_3) +
  \widehat{\ell}_{F, j}^{(k)} (1 + \theta_2) \\
\Longrightarrow \cdb{F}^{(k)} &=
  U_{k + 1} \cdb{F}^{(k + 1)}(1 + \theta_3) +
  \widehat{\ell}_{F}^{(k)} (1 + \theta_2) \\
\Longrightarrow \cdb{F}^{(0)} &=
  \sum_{k = 0}^{n - 1}
  U_1 \cdots U_k \widehat{\ell}_F^{(k)} (1 + \theta_{3k - 1})
  = \sum_{k = 0}^{n - 1}
  \left[\sum_{j = 0}^k \widehat{\ell}_{F, j}^{(k)} (1 + \theta_{3k - 1})
    B_{j, k}(s)\right].
\end{align}
From
\begin{align}
\widehat{\ell}_{F, j}^{(k)} &= e_1 \oplus \cdots \oplus e_{5F - 2} \oplus
\left(\rho \otimes \cdb{F - 1}_j^{(k + 1)}\right) \\
&= e_1\left(1 + \theta_{5F - 2}\right) + \cdots +
e_{5F - 2}\left(1 + \theta_2\right) +
\rho \cdot \cdb{F - 1}_j^{(k + 1)} \left(1 + \theta_2\right) \\
\Longrightarrow \widehat{\ell}_{F, j}^{(k)}\left(1 + \theta_{3k - 1}\right)
&= \ell_{F, j}^{(k)} + \left[e_1 \theta_{3k + 5F - 3} + \cdots +
e_{5F - 2} \theta_{3k + 1} +
\rho \cdot \cdb{F - 1}_j^{(k + 1)} \theta_{3k + 1}\right] \\
&\coloneqq \ell_{F, j}^{(k)} + d_{F, j}^{(k)}
\end{align}
we see that
\begin{equation}
\cdb{F}^{(0)} = \db{F}^{(0)} + \sum_{k = 0}^{n - 1}
  \left[\sum_{j = 0}^k d_{F, j}^{(k)}
B_{j, k}(s)\right]
\end{equation}
hence
\begin{equation}
\left|\db{F + 1}^{(0)}\right| =
\left|\db{F}^{(0)} - \cdb{F}^{(0)}\right|
\leq \sum_{j = 0}^k \left|d_{F, j}^{(k)}\right| B_{j, k}(s).
\end{equation}
To put a bound on this, define the following
``tilde'' notation for a sum: if \(A = \sum_j \alpha_j\) then
\(\widetilde{A} = \sum_j \left|\alpha_j\right|\) (similar notation is used
for \(\widetilde{p}(s)\), which is used in the condition number).
With this, we must have
\begin{equation}
\left|d_{F, j}^{(k)}\right| =
\left|e_1 \theta_{3k + 5F - 3} + \cdots +
e_{5F - 2} \theta_{3k + 1} +
\rho \cdot \cdb{F - 1}_j^{(k + 1)} \theta_{3k + 1}\right|
\leq \gamma_{3k + 5F - 3} \cdot \widetilde{\ell}_{F, j}^{(k)}.
\end{equation}
In addition, one can show that
\begin{alignat}{10}
\widetilde{\ell}_{1, j}^{(k)} &\leq
  && &&
  \gamma_3 \left(
  (1 - s) \left|\widehat{b}_j\right| +
  s \left|\widehat{b}_{j + 1}\right|\right) \\
\widetilde{\ell}_{2, j}^{(k)} &\leq
  \gamma_5 \cdot
  \widetilde{\ell}_{1, j}^{(k)} &&+
  &&
  \gamma_3 \left(
  (1 - s) \left|\cdb{1}_j\right| +
  s \left|\cdb{1}_{j + 1}\right|\right) \\
\widetilde{\ell}_{3, j}^{(k)} &\leq
  \gamma_{10} \cdot
  \widetilde{\ell}_{2, j}^{(k)} &&+
  &&
  \gamma_3 \left(
  (1 - s) \left|\cdb{2}_j\right| +
  s \left|\cdb{2}_{j + 1}\right|\right) \\
\widetilde{\ell}_{F + 1, j}^{(k)} &\leq
  \gamma_{5F} \cdot
  \widetilde{\ell}_{F, j}^{(k)} &&+
  &&
  \gamma_3 \left(
  (1 - s) \left|\cdb{F}_j\right| +
  s \left|\cdb{F}_{j + 1}\right|\right).
\end{alignat}
To be continued...

@@

\section{Appendix: Algorithms}\label{sec:appendix-algo}

@@

\noindent Since the final error \(\cdb{K - 1}\) will not track the errors
during computation, we have a non-EFT version of
Algorithm~\ref{alg:local-error-eft}:

\begin{breakablealgorithm}
  \caption{\textit{Compute the local error (non-EFT).}}
  \label{alg:local-error}

  \begin{algorithmic}
    \Function{\(\widehat{\ell} =
        \mathtt{LocalError}\)}{$e, \rho, \delta b$}
      \State \(L = \texttt{length}(e)\)
      \\
      \State \(\widehat{\ell} = e_1 \oplus e_2\)
      \For{\(j = 3, \ldots, L\)}
        \State \(\widehat{\ell} = \widehat{\ell} \oplus e_j\)
      \EndFor
      \\
      \State \(\widehat{\ell} = \widehat{\ell} \oplus \left(\rho \otimes \delta b\right)\)
    \EndFunction
  \end{algorithmic}
\end{breakablealgorithm}
